---
title: "Example Report"
author: "Abigail ter Kuile"
date: "11/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

```


```{r }
x <- rnorm(2)

for(i in 1:length(x)){
  print(x[[i]])
}
```
```{r}
x <- rbeta (1000, 5, 2)

```
the mean of the observation is `r mean(x)`

# **Old faithful reproducibility exercise** 

# Introduction
The Old Faithful data set contains the waiting time between eruptions and the duration of the eruption for the Old Faithful geyser in Yellowstone National Park, Wyoming, USA.

First load the data:
```{r}
df <- faithful
```

The data description is given in the table below.

| variable | description | 
| - | - |
| eruptions | the duration of the eruption, minutes |
| waiting | waiting time to next eruption, minutes | 


```{r}
summary (df)
```

The marginal distributions of the variables shown below:
```{r}
hist(df$eruptions)
```
```{r}
hist(df$waiting)
```


```{r}
scatter.smooth(df$eruptions, df$waiting)
```

